---
title: "Final Timepoint Model Summaries"
output:
 html_document: 
  code_folding: hide
  toc: yes
  toc_float:
      toc_collapsed: true
---

<style type="text/css">
.main-container {
max-width: 1800px !important;
margin-left: auto;
margin-right: auto;
}
</style>

This markdown/html summarises a set of outer fold models primarily using the 
nested_rocs function in ../../3_Plotting_and_summary_scripts/plotting_scripts.r. This outputs
ROC curves and a table of summaries for all aggregated outer folds. 

<div style="text-align: right"> Load data and libraries ↴ &nbsp; &nbsp; </div>


```{r, warning=FALSE, message=FALSE}
load("/media/gcpeac/R4RA_machine_learning/Data/curated_input.rdata")
source("/media/gcpeac/R4RA_machine_learning/4_Plotting_scripts/plotting_scripts.r")
library(ggplot2)
library(kableExtra)
library(plotROC)
library(pROC)
library(caret)
library(ggpubr)
library(DT)
library(tidyr)
library(dplyr)

knitr::opts_chunk$set(fig.width=12, fig.height=7, warning = FALSE)
```

<div style="text-align: right"> Set up datatable download ↴ &nbsp; &nbsp; </div>

```{r, fig.height=1, out.height=1}
df = rbind(t(data.frame(table(response_df$CDAI50_toc_resp)))[2, ], 
           t(data.frame(table(response_df$CDAI50_rtx_resp)))[2, ], 
           t(data.frame(table(response_df$CDAI50_any_resp)))[2, ])
dimnames(df) = list(c("Tocilizumab", "Rituximab", "Any"), 
                    c("Non-Responder", "Responder"))

# Init Step to make sure that the dependencies are loaded
htmltools::tagList(DT::datatable(df, filter="top", width=900, height = "100%", 
                                 options=list(pageLength=3, lengthChange=FALSE)))
```

<div style="text-align: right"> Load in the models ↴ &nbsp; &nbsp; </div>


```{r}
files = list.files("/media/lvm1/R4RA_ML_outputs/", 
                   full.names = T, recursive = T)
files = c(files, list.files("/home/kgoldmann/Documents/R4RA_ML/Nested/Final", 
                            full.names = T, recursive = T) )
files = files[! grepl("clin_hist", files)]
files = files[! grepl("8781", files)] # can ignore since these converge to the same model
files = files[! grepl("visit7", files)]

l = length(strsplit(files[1],"/")[[1]])

for(x in files) {
  k = gsub(".*_", "", strsplit(x,"/")[[1]][l-1])
  n = gsub(".*_", "", strsplit(x,"/")[[1]][l-2])
  load(x)
  obj = ls(pattern="t_exp")
  for(y in obj){ 
    out = get(y)
    invisible(lapply(1:length(out), function(z) out[[z]]$file <<- x))
    assign(x=paste0(gsub("t_exp", "x_exp", y), "_", k, "_", n), out) 
  }
  rm(list=obj)
}

data=ls(pattern="x_exp")

t_nested = lapply(data, get)

for(x in 1:length(t_nested)) {
  for(j in 1:length(t_nested[[x]])){
    if(class(t_nested[[x]][[j]]) != "try-error"){
      t_nested[[x]][[j]]$type = t_nested[[x]][[j]]$filtering
      t_nested[[x]][[j]]$info = data[x]
    }
  }
}

t_nested = unlist(t_nested, recursive=F)
paste("Removing", length(which(unlist(lapply(t_nested, function(x) class(x[[3]]))) %in% c("try-error", "character"))), "models which failed")

t_nested = t_nested[! unlist(lapply(t_nested, function(x) class(x[[3]])))  %in% c("try-error", "character")]

t_nested = t_nested[unlist(lapply(t_nested, class)) != "try-error"]
names(t_nested) <- unlist(lapply(1:length(t_nested), function(x){
  type <- t_nested[[x]]$info
  gsub("\\.rdata", "", paste0(t_nested[[x]]$models[[1]]$metric, "_", type))
}))

l= length(unlist(strsplit(names(t_nested)[1], "_")))

input_vals = unique(unlist(lapply(names(t_nested), function(x) unlist(strsplit( x, "_"))[l])))
k_vals = unique(unlist(lapply(names(t_nested), function(x) unlist(strsplit(x, "_"))[l-1])))
filt_vals = unique(unlist(lapply(names(t_nested), function(x) unlist(strsplit(x, "_"))[l-3])))
drugs = unique(unlist(lapply(names(t_nested), function(x) unlist(strsplit(x, "_"))[2])))

remove(list = ls(pattern="x_exp"))
gc(verbose=F)
```

# Overall {.tabset .tabset-fade}


```{r, results='asis', warning=FALSE}
df_all = list()

for(inp in input_vals){
  cat("\n\n## No features:", inp, "{.tabset .tabset-fade}" )
  for(drug in drugs){
    name = c("toc"="Tocilizumab", "rtx"="Rituximab", "any"="Refractory")[drug]
    cat("\n\n### ", name, "{.tabset .tabset-fade}" )
    for(filt in filt_vals){
      cat("\n\n\n#### ", filt, "filtering {.tabset .tabset-fade}" )
      k_use = names(t_nested[unlist(lapply(names(t_nested), function(x) unlist(strsplit(x, "_"))[l])) == inp])
      k_use = k_use[grepl(filt, k_use)]
      k_use = k_use[grepl(inp, k_use)]
      k_use = unique(gsub(".*_", "", gsub(paste0("_", inp), "", k_use)))
      for(k_in in k_use){
        cat("\n\n\n##### k=", k_in, "##\n" )
        o = try(nested_rocs(t_nested[unlist(lapply(names(t_nested), function(x) unlist(strsplit(x, "_"))[l])) == inp],
                            metric="CDAI50",  drug=drug, filtering = filt, k=as.numeric(k_in)))
        
        if(class(o) != "try-error"){
          
          o2 = o$stats_df[, ! colnames(o$stats_df) %in% c("Left-out Stats", "Overall Stats")]
          
          o2$Stat = gsub('[[:digit:]]+', '', rownames(o2))
          o2$Stat[o2$Stat == "F"] = "F1"
          
          o2 = o2 %>%
            gather(key = "Set", value = "value", "Test Stats") %>% #, "Left-out Stats", "Overall Stats" ) %>%
            mutate(filtering = unlist(lapply(strsplit(as.character(model), "_"), "[[", l-3)),
                   drug = unlist(lapply(strsplit(as.character(model), "_"), "[[", 2)),
                   model = unlist(lapply(strsplit(as.character(model), "_"), "[[", l-2)))
          
          o3 = o2 %>% group_split(Stat)
          names(o3) = levels(factor(o2$Stat))
          
          o4 = do.call(cbind, o3)
          o4 = o4[, ! grepl("model|Stat|Set|filtering|drug|file", colnames(o4))]
          o4 = cbind(o3[[1]][, c("model","Set",  "filtering", "drug", "file")], o4)
          colnames(o4) = gsub("\\.value", "", colnames(o4))
          
          o4$target_k = k_in
          o4$n_input = inp
          o4 = unique(o4)
          o4 = o4[order(o4$AUC, decreasing = T), ]
          
          temp = o$roc_df[o$roc_df$eval == "test", ]
          temp = temp[! duplicated(temp$model), ]
          
          o4$AUC_roc = temp$auc[match(o4$model, temp$model)]
          
          
          print(htmltools::tagList(
            DT::datatable(o4[, c('model', 'Set', 'filtering', 'drug', 'Accuracy',
                                 'AUC', 'AUC_roc', 'Balanced Accuracy', 'F1', 'Kappa',
                                 'McnemarPValue', 'Precision', 'Prevalence',
                                 'Recall', 'Sensitivity', 'Specificity', 
                                 'Youden_sensitivity', 'Youden_specificity')],
                          filter="top", width=1500, rownames = FALSE,
                          options=list(scrollX=T, pageLength=12,
                                       searchCols = list(NULL, list(search = 'Test Stats'),
                                                         rep(NULL, 13)))) %>%
              formatRound(columns=c('Accuracy', 'AUC','AUC_roc', 'Balanced Accuracy', 'F1', 'Kappa',
                                    'McnemarPValue', 'Precision', 'Prevalence',
                                    'Recall', 'Sensitivity', 'Specificity', 
                                    'Youden_sensitivity', 'Youden_specificity'), digits=3)
          ))
          
          print(o$combined)
          
          o4 = o4[, c('model', 'Set', 'filtering', 'drug', 'Accuracy',
                      "target_k", "final_k", "mean_inner_k", "n_input",
                      'AUC','AUC_roc', 'Balanced Accuracy', 'F1', 'Kappa',
                      'McnemarPValue', 'Precision', 'Prevalence',
                      'Recall', 'Sensitivity', 'Specificity', 
                      'Youden_sensitivity', 'Youden_specificity', 'file')]
          
          
          
          df_all[[length(df_all)+1]] = o4
        }
        
        cat("\n\n" )
      }
      cat("\n\n" )
    }
    cat("\n\n" )
  }
  cat("\n\n" )
}

df = do.call(rbind, df_all)

```
# {.toc-ignore}


# Best models

```{r}
save(df, file="/media/gcpeac/R4RA_machine_learning/Data/all_model_summaries_da.rdata")
df2 = df[df$Set == "Test Stats", ]
df2 = df2[order(df2$AUC, decreasing=T), ]

kable(df2[! duplicated(paste(df2$drug, df2$filtering)), ], row.names = F) %>% 
  kable_styling()
```

# All models 

```{r}

kable(df2, row.names = F) %>% kable_styling()  %>% 
  scroll_box(height = "800px")
```

