---
title: "Initial Timepoint Model Summaries"
output:
 html_document: 
  code_folding: hide
  toc: yes
  toc_float:
      toc_collapsed: true
---

This markdown/html summarises a set of outer fold models primarily using the 
nested_rocs function in ../4_Plotting_and_summary_scripts/plotting_scripts.r. This outputs
ROC curves and a table of summaries for all aggregated outer folds. 

<div style="text-align: right"> Load data and libraries ↴ &nbsp; &nbsp; </div>

```{r, warning=FALSE, message=FALSE}
load("/media/gcpeac/R4RA_machine_learning/Data/curated_input.rdata")
source("/media/gcpeac/Katriona/R4RA/MachineLearning/Github_scripts/3_Plotting_and_summary_scripts/plotting_scripts.r")
library(ggplot2)
library(kableExtra)
library(plotROC)
library(pROC)
library(caret)
library(ggpubr)
library(DT)
library(tidyr)
library(dplyr)

knitr::opts_chunk$set(fig.width=12, fig.height=7)
```

<div style="text-align: right"> Set up datatable download ↴ &nbsp; &nbsp; </div>

```{r, fig.height=1, out.height=1}
temp = response_df$overall_response_CDAI50
temp[response_df$swtrt == "RITtoTOC"] = "RNR"
temp[response_df$swtrt == "TOCtoRIT"] = "TNR"

temp = data.frame(table(gsub("\\_.*", "", temp)))
df = data.frame("Non-Responder"=c(temp$Freq[temp$Var1 == "TNR"], 
                                  temp$Freq[temp$Var1 == "RNR"]), 
                "Responder"=c(temp$Freq[temp$Var1 == "TR"], 
                              temp$Freq[temp$Var1 == "RR"]), check.names = F)
rownames(df) = c("Tocilizumab", "Rituximab")

# Init Step to make sure that the dependencies are loaded
htmltools::tagList(DT::datatable(df, filter="top", width=900, height = "100%", 
                                 options=list(pageLength=3, lengthChange=FALSE)))
```

<div style="text-align: right"> Load in the models ↴ &nbsp; &nbsp; </div>


```{r}
files = list.files("/media/lvm1/R4RA_ML_outputs/Baseline", 
                   pattern="all_visit7_ml_nested", 
                   full.names = T, recursive = T)

for(x in files) {
  k = gsub(".*_", "", strsplit(x,"/")[[1]][7])
  n = gsub(".*_", "", strsplit(x,"/")[[1]][6])
  load(x)
  obj = ls(pattern="t_exp")
  
  for(y in obj){ 
     out = get(y)
    invisible(lapply(1:length(out), function(z) out[[z]]$file <<- x))
    assign(x=paste0(gsub("t_exp", "x_exp", y), "_", k, "_", n), out) 
  }
  rm(list=obj)
}

data=ls(pattern="x_exp")

t_nested = lapply(data, get)
for(x in 1:length(t_nested)) {
  for(j in 1:length(t_nested[[x]])){
    if(class(t_nested[[x]][[j]]) != "try-error"){
      t_nested[[x]][[j]]$type = t_nested[[x]][[j]]$filtering
      t_nested[[x]][[j]]$info = data[x]
    }
  }
}
t_nested = unlist(t_nested, recursive=F)
paste("Removing", length(which(unlist(lapply(t_nested, class)) == "try-error")), "models which failed")

t_nested = t_nested[unlist(lapply(t_nested, class)) != "try-error"]


names(t_nested) <- unlist(lapply(1:length(t_nested), function(x){
  type <- t_nested[[x]]$info
  paste0(t_nested[[x]]$models[[1]]$metric, "_", gsub("_NA", paste0("_", unique(t_nested[[1]]$df$n_output_genes)), type))
}))

t_nested= t_nested[grepl("toc|rtx", names(t_nested))]
# remove the glmnet which looked really good in test stats but not LO
#t_nested = t_nested[names(t_nested) != "CDAI50_toc_resp_x_exp_and_clin_none_glmnet_100_1438"]
#names(t_nested) = gsub("none2", "none", names(t_nested) )

input_vals = unique(unlist(lapply(names(t_nested), function(x) unlist(strsplit(x, "_"))[11])))
k_vals = unique(unlist(lapply(names(t_nested), function(x) unlist(strsplit(x, "_"))[10])))
filt_vals = unique(unlist(lapply(names(t_nested), function(x) unlist(strsplit(x, "_"))[8])))
drugs = unique(unlist(lapply(names(t_nested), function(x) unlist(strsplit(x, "_"))[2])))
```

# Overall {.tabset .tabset-fade}

```{r, results='asis', warning=FALSE}
df_all = list()

for(inp in input_vals){
  cat("\n\n## No features:", inp, "{.tabset .tabset-fade}" )
  for(drug in drugs){
    name = c("toc"="Tocilizumab", "rtx"="Rituximab", "any"="Refractory")[drug]
    cat("\n\n### ", name, "{.tabset .tabset-fade}" )
    for(filt in filt_vals){
      cat("\n\n\n#### ", filt, "filtering {.tabset .tabset-fade}" )
      k_use = names(t_nested[unlist(lapply(names(t_nested), function(x) unlist(strsplit(x, "_"))[11])) == input_vals])
      k_use = k_use[grepl(filt, k_use)]
      k_use = unique(gsub(".*_", "", gsub(paste0("_", inp), "", k_use)))
      
      for(k_in in k_use){
        cat("\n\n\n##### k=", k_in, "##\n" )
        o = try(nested_rocs(
          modelList = t_nested[unlist(lapply(names(t_nested), function(x) {
            unlist(strsplit(x, "_"))[11] == input_vals & unlist(strsplit(x, "_"))[8] == filt
            }))], metric="CDAI50",  drug=drug, 
          filtering = filt, k=as.numeric(k_in) ))
        
        if(class(o) != "try-error"){
          
          # group the stats together
          o2 = o$stats_df
          o2$k = gsub(".*_", "", o2$model)
          
          o2$Stat = gsub('[[:digit:]]+', '', rownames(o2))
          o2$Stat[o2$Stat == "F"] = "F1"
          
          o2 = o2 %>%
            gather(key = "Set", value = "value", "Test Stats", 
                   "Left-out Stats", "Overall Stats" ) %>%
            mutate(filtering = unlist(lapply(strsplit(as.character(model), "_"), "[[", 8)),
                   drug = unlist(lapply(strsplit(as.character(model), "_"), "[[", 2)),
                   model = unlist(lapply(strsplit(as.character(model), "_"), "[[", 9)))
          
          o3 = o2 %>% group_split(Stat)
          names(o3) = levels(factor(o2$Stat))
          
          o4 = do.call(cbind, o3)
          o4 = o4[, ! grepl("model|Stat|Set|filtering|drug", colnames(o4))]
         
          o4 = cbind(o3[[1]][, c("model","Set",  "filtering", "drug", "file")], o4)
          colnames(o4) = gsub("\\.value", "", colnames(o4))
          
          o4 = o4[order(o4$AUC, decreasing = T), ]
          
          
          
          print(htmltools::tagList(
            DT::datatable(o4[, c('model', 'Set', 'filtering', 'drug', 'Accuracy',
                                 'AUC', 'Balanced Accuracy', 'F1', 'Kappa',
                                 'McnemarPValue', 'Precision', 'Prevalence',
                                 'Recall', 'Sensitivity', 'Specificity', 
                                    'Youden_sensitivity', 'Youden_specificity')],
                          filter="top", width=1500, rownames = FALSE,
                          options=list(scrollX=T, pageLength=12,
                                       searchCols = list(NULL, list(search = 'Test Stats'),
                                                         rep(NULL, 13)))) %>%
              formatRound(columns=c('Accuracy', 'AUC', 'Balanced Accuracy', 'F1', 'Kappa',
                                    'McnemarPValue', 'Precision', 'Prevalence',
                                    'Recall', 'Sensitivity', 'Specificity', 
                                    'Youden_sensitivity', 'Youden_specificity'), digits=3)
          ))
          
          print(o$combined)
          
          
          o4$target_k = k_in
          o4$n_input = inp
          
          o4 = o4[, c('model', 'Set', 'filtering', 'drug', 'Accuracy',
                      "target_k", "final_k", "mean_inner_k", "n_input",
                      'AUC', 'Balanced Accuracy', 'F1', 'Kappa',
                      'McnemarPValue', 'Precision', 'Prevalence',
                      'Recall', 'Sensitivity', 'Specificity', 
                      'Youden_sensitivity', 'Youden_specificity', 'file')]
          
          
          df_all[[length(df_all)+1]] = o4
        }
        
        
        
        
        cat("\n\n" )
      }
      cat("\n\n" )
    }
    cat("\n\n" )
  }
  cat("\n\n" )
}

# Combine all outputs
df = do.call(rbind, df_all)

```

# Best models

```{r}
#save(df, file="/media/gcpeac/R4RA_machine_learning/Data/all_baseline_model_summaries2.rdata")
df$AUC = as.numeric(as.character(df$AUC))
df2 = df[df$Set == "Test Stats", ]

df2 = df2[order(df2$AUC, decreasing=T), ]

kable(df2[! duplicated(paste(df2$drug, df2$filtering)), ], row.names = F) %>% 
  kable_styling()
```

# All models 

```{r}
kable(df2, row.names = F) %>% kable_styling()  %>% 
  scroll_box(height = "800px")
```