---
title: "Best Gene Expression Models"
author: "Katriona Goldmann"
date: "8/19/2021"
output: 
 html_document: 
  code_folding: hide
  toc: yes
  toc_float:
      toc_collapsed: true
---

```{r setup, include=FALSE}
library(ggplot2)
library(kableExtra)
library(plotROC)
library(pROC)
library(caret)
library(ggpubr)
library(DT)
library(rmarkdown)
library(tidyr)
library(dplyr)
library(gbm)
set.seed(1234)

knitr::opts_chunk$set(echo = TRUE, cache=FALSE, fig.width=14, 
                      fig.height=10, warning = FALSE)
```

To annotate features you will need a [disGenNet api key](https://www.disgenet.org/api/). See ↓ to set up key

```{r}
# requires disGenNet credentials for gene annotations
#devtools::install_github("KatrionaGoldmann/omicAnnotations")
if(Sys.getenv("api_key_user") != "" & Sys.getenv("api_key_password") != "") {
  api_key = omicAnnotations::get_api_key(Sys.getenv("api_key_user"), 
                                         Sys.getenv("api_key_password"))
} else {api_key = NULL}
```


# Scripts

```{r}
inner_folds_n=1

# function to perform univariate filtering
univariate_filtering = function(sdata, train_control, size){
  filterCtrl <- sbfControl(functions = rfSBF)
  
  predictors = sdata[, colnames(sdata) != "resp"]
  
  rfe_out <- sbf(x = predictors,
                 y = sdata$resp,
                 sbfControl = filterCtrl,
                 trControl=train_control)
  
  # subset by the number of times each feature is selected (min in size)
  nsize = min(size, length(predictors(rfe_out)), na.rm=T)
  min_n = min(sort(table(unlist(rfe_out$variables)), decreasing = T)[1:nsize]) # pick those which appear most
  features = names(table(unlist(rfe_out$variables)))[table(unlist(rfe_out$variables)) >= min_n]
  
  subdata <- sdata[, c(features, "resp")]
  return(subdata)
}


# function to perform filtering via recursive feature elimintation
rfe_filtering = function(sdata, rfe_funcs, size, ml_method, 
                         eval_metric="Accuracy", train_control){
  rfe.ctrl = rfeControl(functions = rfe_funcs,
                        #method = "repeatedcv",
                        allowParallel =TRUE, 
                        verbose = FALSE)
  
  predictors = sdata[, colnames(sdata) != "resp"]
  
  rfe_out <- rfe(x = predictors, 
                 y = sdata$resp, 
                 sizes = size,
                 method=ml_method, 
                 metric = eval_metric, 
                 rfeControl = rfe.ctrl, 
                 trControl=train_control)
  
  subdata <- sdata[, c(predictors(rfe_out), "resp")]
  return(subdata)
}

clin_cols = c('TJC', 'SJC', 'CDAI', 'DAS28.CRP', 'DAS28.ESR', 'Age', 'Gender', 
              'ESR', 'CRP', 'CD20', 'CD138', 'CD68L', 'CD68SL', 'CD3')


# For each model output the summary stats, roc curves, variable importance
outputs <- function(model, df3, header_level="####"){
  
  cat("\n\n\n\n</br></br>")  
  cat("\n\n\n\n\n\n", header_level, " Model Summary\n")
  
  cat(paste("\n\n\U2022 Using", model$filtering, "filtering"))
  cat(paste0("\n\n\U2022 Number of features in each fold: ", 
             paste(lapply(model$models, function(x) length(x$selected_features)), 
                   collapse=", ")))
  cat(paste("\n\n\U2022 Average test AUC on outer folds <b>", 
            format( model$auc, digit=3), "</b>"))
  cat(paste("\n\n\U2022 Average balanced accuracy on outer folds <b>",
            format(mean(model$df$Balanced.Accuracy), digit=3), "</b>\n\n\n"))
  
  all_folds = do.call(rbind, lapply(model$models, function(x) x$prob))
  total_auc = auc(all_folds$observed, all_folds$R, levels=c("NR", "R"), direction="<")
  cat(paste("\n\n\U2022 AUC on all test-set predictions from all outer folds<b>", 
            format(total_auc, digits=3), "</b>\n\n"))
  
  
  inner_folds = do.call(rbind, lapply(model$models, function(x) {
    rfFit = x$fit
    accuracy_lo = rfFit$results
    lo_df = rfFit$pred
    for(colu in colnames(rfFit$bestTune)){
      accuracy_lo = accuracy_lo[accuracy_lo[, colu] == rfFit$bestTune[, colu], ]
      lo_df = lo_df[lo_df[, colu] == rfFit$bestTune[, colu], ]
    }
    return(lo_df)
  }))
  inner_auc = auc(inner_folds$obs, inner_folds$R, levels=c("NR", "R"), direction="<")
  cat(paste("\n\n\U2022 AUC on all left-out-set predictions from all outer folds<b>", 
            format(inner_auc, digits=3), "</b>\n\n"))
  
  
  model$df$mean_inner_n = unlist(lapply(model$models, function(x) {
    length(which(varImp(x$fit)$importance$Overall != 0))
  }))
  
  
  # output the ROC curves
  cat("\n\n\n\n\n\n", header_level, " ROC curves\n")
  
  po = ggplot(all_folds, aes(d = observed, m = R)) +
    geom_roc(labels=F, pointsize=0, linemitre=1, color="dodgerblue") +
    geom_abline(slope=1, intercept=0, color="grey60", linetype="dashed") + 
    labs(x="1 - Specificity", y="Sensitivity", title = "Test Set") + 
    annotate("text", x=1, y=0.1,  hjust = 1, size=5, 
             label=paste0("AUC = ", format(total_auc, digits=3))) + 
    theme_classic() + 
    theme(text = element_text(size=15))
  
  pi = ggplot(inner_folds, aes(d = obs, m = R)) +
    geom_roc(labels=F, pointsize=0, linemitre=1, color="gold2") +
    geom_abline(slope=1, intercept=0, color="grey60", linetype="dashed") + 
    labs(x="1 - Specificity", y="Sensitivity", title = "Left-Out Set") + 
    theme_classic() + 
    annotate("text", x=1, y=0.1,  hjust = 1, size=5, 
             label=paste0("AUC = ", format(inner_auc, digits=3))) + 
    theme(text = element_text(size=15))
  
  print(ggarrange(po, pi, ncol=2, nrow=1))
  
  # Interogate the feature data
  feat = data.frame(table(unlist(lapply(model$models, function(x) x$selected_features))))
  feat = feat[order(feat$Freq, decreasing = T), ]
  feat = feat[feat$Freq > 1, ]
  feat$type="Gene"
  feat$type[feat$Var1 %in% clin_cols] = "Clinical"
  
  # Option to annotate the features
  # df = omicAnnotations::gene_summary(feat$Var1, disease_api_token = api_key, 
  #                                    gene_description = FALSE)
  # feat = cbind(feat, df[match(feat$Var1, df$Gene),
  #                      c("Type", "Curated_description", 
  #                        "Associated_diseases")])
  
  cat("\n\n\n\n\n\n", header_level, " Features selected in each fold\n")
  print(kable(feat, row.names = F) %>% kable_styling() %>% 
          scroll_box(height = "400px"))
  
  mod = model$models
  
  bestTune = do.call(rbind, lapply(mod, function(x) x$fit$bestTune))
  bestTune$k = unlist(lapply(model$models, function(x) {
    length(which(varImp(x$fit)$importance != 0))
  }))
  
  # Output the tuning parameters
  cat("\n\n\n", header_level, " Best Tuned Parameters\n")
  rownames(bestTune) = paste("Fold", 1:nrow(bestTune))
  bestTune = rbind(bestTune, "Average"=apply(bestTune, 2, mean))
  print(kable(bestTune) %>% kable_styling())
  

  # Set up the feature space
  tvst <- data.frame(exp_sd)
  # add response variable
  tvst$resp = factor(clinical$CDAI50_toc_resp, labels=c("NR", "R"))
  tvst = tvst[! is.na(tvst$resp), ]
  
  # train and fit on entire data set
  train_control <- trainControl(method="none",
                                classProbs = TRUE,
                                savePredictions = TRUE)
  
  
  # Filter and subset the data
  if(model$filtering == "univariate"){
    subdata = univariate_filtering(tvst, train_control,
                                   size=as.numeric(gsub(".*\\_", "", model$info)))
  } else if(model$filtering == "rfe"){
    
    subdata = rfe_filtering(tvst, rfe_funcs = caretFuncs,
                            train_control = train_control, 
                            ml_method = mod[[1]]$fit$method,
                            eval_metric="Accuracy",
                            size=as.numeric(gsub(".*\\_", "", model$info)))
  } else{subdata = tvst}
  
  # degree must be an integer
  if("degree" %in% colnames(bestTune)){
    bestTune["Average", "degree"] = 
      round(mean(bestTune[rownames(bestTune) != "Average", "degree"]))
  }
  
  # fit on full data set
  fit <- try(caret::train(resp ~.,
                          data=subdata,
                          method = mod[[1]]$fit$method,
                          metric = "Accuracy",
                          trControl = train_control,
                          tuneGrid = bestTune["Average", colnames(bestTune) != 
                                                "k", drop=F],
                          preProcess=NULL))
  
  
  if(class(fit) == "try-error"){
    return(  return(list("test_roc"=po, "lo_roc"=pi,  
                         "bestTune"=bestTune, "all"=model)))
  } else {
    # variable importance
    vi = varImp(fit)
    vi =  data.frame(as.matrix(vi$importance))
    colnames(vi)[1] = "Overall"
    vi$gene = rownames(vi)
    vi = vi[order(abs(vi$Overall), decreasing = T), ]
    
    # Annotate features if api key is available
    if(! is.null(api_key)){
      df = omicAnnotations::gene_summary(gsub("\\.AS", "-AS",rownames(vi)),
                                         disease_api_token = api_key,
                                         gene_description = F)
      vi = cbind(vi, df)
    }
    
    cat("\n\n", header_level, " Variable Importance \n")
    cat(paste("<b>Number of features importance !=0: ", 
              length(which(vi$Overall != 0)), "</b>\n\n"))
    print(kable(vi[, colnames(vi) != "Curated_description"], row.names = F) %>% 
            kable_styling() %>% scroll_box(height = "400px"))
    
    vie = vi[vi$Overall != 0, ]
    vie$gene = factor(vie$gene, levels=rev(unique(vie$gene)))
    
    p1 =  ggplot(vie, aes(y=Overall, x=gene)) +
      geom_bar(stat="identity", fill="midnightblue") +
      coord_flip() +
      labs(y="Importance", x="") +
      theme_classic() + 
      theme(text=element_text(size=20), 
            legend.position="none", 
            panel.grid = element_line(colour = "grey92"),
            panel.grid.minor = element_line(size = rel(0.5)), 
            panel.grid.major = element_line(size = rel(0.7))) 
    print(ggarrange(ggplot(data=NULL) + theme_void(), p1, ncol=3, 
                    widths=c(1, 2, 1)))
    
    # If glmnet output the coefficient plot as well
    if(mod[[1]]$fit$method == "glmnet"){
      cat("\n\n", header_level, " Coefficients \n")
      
      tmp_coeffs <- coef(fit$finalModel, s = fit$bestTune$lambda)
      
      coefs = data.frame(as.matrix(tmp_coeffs))
      colnames(coefs)="coef"
      coefs$gene = rownames(coefs)
      coefs = coefs[order(abs(coefs$coef), decreasing = T), ]
      cat(paste("<b>Number of features following sparcity filter: ", 
                length(which(coefs$coef != 0)), "</b>\n\n"))
      
      coefs[coefs == 0] = "."
      print(kable(coefs, row.names = F) %>% kable_styling() %>% 
              scroll_box(height = "400px"))
      
      coefs[coefs == "."] = 0
      if(nrow(coefs) > 50) co = coefs[1:50, ]
      co$gene = factor(co$gene, levels=rev(unique(co$gene)))
      
      co$dir = unlist(lapply(as.numeric(co$coef), function(x) x/abs(x)))
      co = co[co$coef != 0, ]
      
      
      p2 = ggplot(co, aes(y=as.numeric(coef), x=gene, fill=factor(dir))) +
        geom_bar(stat="identity") +
        scale_fill_manual(values=c("midnightblue", "firebrick1")) + 
        coord_flip() +
        labs(y="Coefficient", x="") +
        theme_classic() + 
        theme(text=element_text(size=20), 
              legend.position = "none",
              panel.grid = element_line(colour = "grey92"),
              panel.grid.minor = element_line(size = rel(0.5)), 
              panel.grid.major = element_line(size = rel(0.7))) 
      
      
      print(ggarrange(ggplot(data=NULL) + theme_void(), p2, ncol=3, 
                      widths=c(1, 2, 1)))
    } else{
      p2 = ggplot(data=NULL) + theme_void()
      coefs=NULL
    }
    
    return(list("test_roc"=po, "lo_roc"=pi, "variable_importance"=p1, 
                "coefficients"=p2, "fit"=fit, "vi"=vi, "coef"=coefs, 
                "bestTune"=bestTune, "all"=model))
  }
}

```

# Best Models at Final Timepoint


```{r}
load("/media/gcpeac/R4RA_machine_learning/Data/all_model_summaries_da.rdata")
df2 = df[df$Set == "Test Stats", ]
df2 = df2[! grepl("none", df2$filtering) | df2$model == "glmnet", ] # no filtering sparce only
df2 = df2[df2$filtering != "rfe", ]

df2 = df2[order(df2$n_input, decreasing = F), ]
df2 = df2[order(df2$target_k, decreasing = T), ]
df2 = df2[order(df2$AUC, decreasing = T), ]

invisible(lapply(c("AUC", "Accuracy", "Balanced Accuracy", "Sensitivity", "Specificity"), function(x){
  df2[, x] <<- format(as.numeric(df2[, x]), digits=3)
}))


df2$nominal_k = df2$target_k
df2$target_k[df2$filtering == "none|none2"] = df2$n_input[df2$filtering == "none|none2"]


kable(df2[, c('model', 'filtering', 'drug', 'Accuracy', 'AUC', 
              'Balanced Accuracy', 'Sensitivity', 'Specificity', 
              'Youden_sensitivity', 'Youden_specificity', 
              'target_k', 'n_input')], row.names = F) %>% kable_styling()
```

```{r}
u = df2

invisible(lapply(1:nrow(u), function(x){
  load(u$file[x], .GlobalEnv)
  i = length(ls(pattern=u$drug[x], envir=.GlobalEnv))
  assign(paste0(u$drug[x], stringr::str_pad(i+1, width=2, pad="0")), 
         get(paste0("t_exp_and_clin_", u$filtering[x], "_", 
                    u$model[x]))[[which(c("toc", "rtx", "any") == u$drug[x])]], 
         envir=.GlobalEnv)
}))

df_final_response = df2

gdata::keep(outputs, univariate_filtering, rfe_filtering, api_key, 
            clin_cols, df_final_response, inner_folds_n,
            list=c(ls(pattern="rtx"), ls(pattern="toc"), ls(pattern="any")), 
            sure=T)
load("/media/gcpeac/R4RA_machine_learning/Data/curated_input.rdata")
```

## Best TOC models {.tabset .tabset-fade}

```{r, results='asis'}
toc_other_filt_plots <- lapply(ls(pattern="toc")[! grepl("other", ls(pattern="toc"))], function(x) {
  cat("\n\n")
  cat(paste0("### Next Best TOC Model (", 
             as.character(unique(get(x)$df$model)), 
             ") {.tabset .tabset-fade} \n\n"))
  temp = outputs(get(x))
  cat("\n\n")
  cat("### {.toc-ignore} \n\n")
  return(temp)
})
```

## {.toc-ignore}

## Best RTX models {.tabset .tabset-fade}

```{r, results='asis'}
rtx_other_filt_plots <- lapply(ls(pattern="rtx")[! grepl("other", ls(pattern="rtx"))], function(x) {
  cat("\n\n")
  cat(paste0("### Next Best RTX Model (", 
             as.character(unique(get(x)$df$model)), 
             ") {.tabset .tabset-fade} \n\n"))
  temp = outputs(get(x))
  cat("\n\n")
  cat("### {.toc-ignore} \n\n")
  return(temp)
})
```

## {.toc-ignore}

## Best Refractory Model {.tabset .tabset-fade}

```{r, results='asis'}
any_other_filt_plots <- lapply(ls(pattern="any")[! grepl("other", ls(pattern="any"))], function(x) {
  cat("\n\n")
  cat(paste0("### Next Best Refractory Model (", 
             as.character(unique(get(x)$df$model)), 
             ") {.tabset .tabset-fade} \n\n"))
  temp = outputs(get(x))
  cat("\n\n")
  cat("### {.toc-ignore} \n\n")
  return(temp)
})
```

## {.toc-ignore}

## Overall Models Selected for Secondary Timepoint

```{r}
df_final_response$fold_k = df_final_response$final_k
df_final_response$final_k = NA

df_final_response$final_k[df_final_response$drug == "toc"] = unlist(lapply(toc_other_filt_plots, function(x) length(x$fit$coefnames)))
df_final_response$final_k[df_final_response$drug == "rtx"]  = unlist(lapply(rtx_other_filt_plots, function(x) length(x$fit$coefnames)))
df_final_response$final_k[df_final_response$drug == "any"] = unlist(lapply(any_other_filt_plots, function(x) length(x$fit$coefnames)))

df_final_response$sparce_k = NA
df_final_response$sparce_k[df_final_response$drug == "toc"] = unlist(lapply(toc_other_filt_plots, function(x) length(which(x$variable_importance$data$Overall != 0))))
df_final_response$sparce_k[df_final_response$drug == "rtx"] = unlist(lapply(rtx_other_filt_plots, function(x) length(which(x$variable_importance$data$Overall != 0))))
df_final_response$sparce_k[df_final_response$drug == "any"] = unlist(lapply(any_other_filt_plots, function(x) length(which(x$variable_importance$data$Overall != 0))))


kable(df_final_response[, c('model', 'filtering', 'drug', 'Accuracy', 'AUC',
                            'Balanced Accuracy', 'Sensitivity', 'Specificity',
                            'target_k', 'final_k','sparce_k', 'n_input')], row.names = F) %>% kable_styling()

```


# Best Models at Initial Timepoint


```{r}
load("/media/gcpeac/R4RA_machine_learning/Data/all_baseline_model_summaries2.rdata")
df2 = df[df$Set == "Test Stats", ]
df2 = df2[! df2$filtering %in% c("none2", "none") | df2$model == "glmnet", ] # no filtering sparce only

df2 = df2[order(df2$n_input, decreasing = F), ]
df2 = df2[order(df2$AUC, decreasing = T), ]

invisible(lapply(c("AUC", "Accuracy", "Balanced Accuracy", "Sensitivity", "Specificity"), function(x){
  df2[, x] <<- format(as.numeric(df2[, x]), digits=3)
}))

df2$nominal_k = df2$target_k
df2$target_k[df2$filtering == "none"] = df2$n_input[df2$filtering == "none"]

df2 = unique(df2)

kable(df2[, c('model', 'filtering', 'drug', 'Accuracy', 'AUC',
              'Balanced Accuracy', 'Sensitivity', 'Specificity',
              'target_k', 'final_k', 'n_input')], row.names = F) %>% kable_styling()
```

```{r}
u = df2

invisible(lapply(1:nrow(u), function(x){
  load(u$file[x], .GlobalEnv)
  i = length(ls(pattern=paste0(u$drug[x], "_bl"), envir=.GlobalEnv))
  assign(paste0(u$drug[x], "_bl", stringr::str_pad(i+1, width=2, pad="0")), get(paste0("t_exp_and_clin_", u$filtering[x], "_", u$model[x]))[[which(c("toc", "rtx", "any") == u$drug[x])]], envir=.GlobalEnv)
}))

df_initial_response = df2

gdata::keep(outputs, univariate_filtering, 
            rfe_filtering, api_key, clin_cols, rtx_other_filt_plots, 
            toc_filt_plots, any_filt_plots, df_final_response, inner_folds_n,
            df_initial_response, list=c(ls(pattern="rtx"), ls(pattern="toc"), ls(pattern="any")), 
            sure=T)
load("/media/gcpeac/R4RA_machine_learning/Data/curated_input.rdata")
```


## Best TOC Initial models {.tabset .tabset-fade}

```{r, results='asis'}
toc_bl_other_filt_plots <- lapply(ls(pattern="toc_bl")[! grepl("other", ls(pattern="toc_bl"))], function(x) {
  cat("\n\n")
  cat(paste0("### Next Best Initial TOC Model (", 
             as.character(unique(get(x)$df$model)), 
             ") {.tabset .tabset-fade} \n\n"))
  temp = outputs(get(x))
  cat("\n\n")
  cat("### {.toc-ignore} \n\n")
  return(temp)
})
```

## {.toc-ignore}



## Best RTX Initial models {.tabset .tabset-fade}

```{r, results='asis'}
rtx_bl_other_filt_plots <- lapply(ls(pattern="rtx_bl")[! grepl("other", ls(pattern="rtx_bl"))], function(x) {
  cat("\n\n")
  cat(paste0("### Next Best Initial RTX Model (", 
             as.character(unique(get(x)$df$model)), 
             ") {.tabset .tabset-fade} \n\n"))
  temp = outputs(get(x))
  cat("\n\n")
  cat("### {.toc-ignore} \n\n")
  return(temp)
})
```

## Overall Models Selected

```{r}
df_initial_response$fold_k = df_initial_response$final_k
df_initial_response$final_k = NA

df_initial_response$final_k[df_initial_response$drug == "toc"] = unlist(lapply(toc_bl_other_filt_plots, function(x) length(x$fit$coefnames)))
df_initial_response$final_k[df_initial_response$drug == "rtx"] = unlist(lapply(rtx_bl_other_filt_plots, function(x) length(x$fit$coefnames)))

df_initial_response$sparce_k = NA
df_initial_response$sparce_k[df_initial_response$drug == "toc"] = unlist(lapply(toc_bl_other_filt_plots, function(x) length(which(x$variable_importance$data$Overall != 0))))
df_initial_response$sparce_k[df_initial_response$drug == "rtx"] = unlist(lapply(rtx_bl_other_filt_plots, function(x) length(which(x$variable_importance$data$Overall != 0))))

kable(df_initial_response[, c('model', 'filtering', 'drug', 'Accuracy', 'AUC',
                              'Balanced Accuracy', 'Sensitivity', 'Specificity',
                              'target_k', 'final_k','sparce_k', 'n_input')], row.names = F) %>% kable_styling()

```

## {.toc-ignore}

# Overlapping Features

Now lets see if there are any features common to multiple models. Currently these chunk are set to eval=FALSE, to run switch this to TRUE

```{r, eval=FALSE}
library(UpSetR)
listInput <- list("Initial Rituximab" = as.character(rtx_bl_other_filt_plots[[1]]$variable_importance$data$gene),
                  "Initial Tocilizumab" = as.character(toc_bl_other_filt_plots[[1]]$variable_importance$data$gene),
                  "Final Rituximab" = as.character(rtx_other_filt_plots[[5]]$variable_importance$data$gene),
                  "Final Tocilizumab" = as.character(toc_other_filt_plots[[1]]$variable_importance$data$gene),
                  "Refractory" = as.character(any_other_filt_plots[[1]]$variable_importance$data$gene))

qs1 = list(
  list(query = UpSetR::intersects, params = list("Initial Rituximab"), color = "royalblue", active = T),
  list(query = UpSetR::intersects, params = list("Initial Tocilizumab"), color = "gold2", active = T),
  list(query = UpSetR::intersects, params = list("Initial Tocilizumab", "Initial Rituximab"),
       color = "mediumseagreen", active = T)
)

qs = list(
  # list(query = UpSetR::intersects, params = list("Final Rituximab"),
  #      color = "royalblue", active = T)#,
  list(query = UpSetR::intersects, params = list("Final Tocilizumab"),
        color = "gold2", active = T),
  list(query = UpSetR::intersects, params = list("Refractory"),
        color = "firebrick1", active = T),
  list(query = UpSetR::intersects, params = list("Final Tocilizumab", "Final Rituximab"),
        color = "mediumseagreen", active = T),
  list(query = UpSetR::intersects, params = list("Refractory", "Final Tocilizumab"),
        color = "#db7918", active = T),
  list(query = UpSetR::intersects, params = list("Refractory", "Final Rituximab"),
        color = "darkorchid", active = T)
)

cat("The intersect between initial Toc and Rtx features: ",
    paste(listInput[[1]], listInput[[2]], collapse=", "))
cat("The intersect between final Toc and Rtx features: ",
    paste(listInput[[3]], listInput[[4]], collapse=", "))

upset(fromList(listInput[1:2]), order.by = "freq", queries = qs1,
      text.scale = 2,
      sets.bar.color = c("gold2", "royalblue"))

upset(fromList(listInput[3:5]), order.by = "freq", text.scale = 2,
      queries = qs,
      main.bar.color = "darkgrey",
      sets.bar.color = c("firebrick1",  "gold2", "royalblue"))
```

Overlap with nanostring

```{r, eval=FALSE}
ns = read.csv("/media/gcpeac/R4RA_machine_learning/Data/CDR-QMUL_1-44030_Design Data.tsv", sep="\t")

listInput2 <- c(listInput, list("nanostring"=as.character(ns$Customer.Identifier)))



upset(fromList(listInput2[c(1:2, 6)]), order.by = "freq",
      text.scale = 2)

upset(fromList(listInput2[3:6]), order.by = "freq", text.scale = 2,
      main.bar.color = "darkgrey")


cat("Nanostring genes which are also TOC features: ",
    paste(listInput2$nanostring[listInput2$nanostring %in% unlist(listInput)], collapse=", "), "\n")
cat("Nanostring genes which are also RTX features: ",
    paste(listInput2$nanostring[listInput2$nanostring %in% c(listInput$`Initial Rituximab`, listInput$`Final Rituximab`)], collapse=", "), "\n")


notoc=unique(c(listInput$`Initial Tocilizumab`, listInput$`Final Tocilizumab`)[! c(listInput$`Initial Tocilizumab`, listInput$`Final Tocilizumab`) %in% listInput2$nanostring])
nortx=unique(c(listInput$`Initial Rituximab`, listInput$`Final Rituximab`)[! c(listInput$`Initial Rituximab`, listInput$`Final Rituximab`) %in% listInput2$nanostring])

cat("TOC features not in nanostring genes (n=", length(notoc), "): ",
    paste(notoc, collapse=", "), "\n")
cat("RTX features not in nanostring genes (n=", length(nortx), "): ",
    paste(nortx, collapse=", "), "\n")


```


Check for feature set enrichment

```{r, message=FALSE, warning=FALSE, results='hide', echo=FALSE, eval=FALSE}
library(omicAnnotations)
library(enrichR)

enrich_list = c(listInput,
                "Initial Response (Rtx-Toc Overlap)"=
                  list(intersect(listInput$`Initial Rituximab`, listInput$`Initial Tocilizumab`)),
                "Final Response (Rtx-Toc-Refractory Overlap)"=
                  list(intersect(intersect(listInput$`Final Rituximab`, listInput$`Final Tocilizumab`), listInput$Refractory) ))

out = invisible(lapply(enrich_list, function(x) {
  temp =  suppressMessages(
    enriched_pathways(as.character(x), cutoff=1, min_N=2,
                      libraries = c('Pathways', 'Ontologies', 'Diseases_Drugs', 'Cell_Types')))

  edf = temp$enrichment
  edf = edf[edf$Adjusted.P.value <= 0.05, ]
  edf = edf[! grepl("LINCS|ARCHS4", edf$Library), ]
  edf = edf[! grepl("Table", edf$Term), ]

  return(edf)
}))

names(out) <- names(enrich_list)
```


```{r, results='hide', echo=FALSE, cache=FALSE, eval=FALSE}
library(RColorBrewer)
library(ggplot2)

plot.list <- invisible(lapply(names(out), function(x){

  edf = out[[x]]
  edf = edf[! grepl("DOI|GSE|Gr5|MODULE|GeneList|14d AA|MGS|Murine|gse|Fig|SKIN|table|Complement|vagina|mucus|Top100|microbial|Estrogen|BREAST|uterus|breast|GTEX|cardiac|oxygen|gland", edf$Term), ]
  edf = edf[! grepl("Mouse", edf$Library), ]
  edf$Term[grepl("GTEX", edf$Term)] = unlist(lapply(edf$Term[grepl("GTEX", edf$Term)], function(x) {
    paste("GTEX:", paste(unlist(strsplit(x, " "))[2:(length(unlist(strsplit(x, " ")))-2)], collapse=" "))
  }))
  edf = edf[edf$Library != "MGI_Mammalian_Phenotype_2017", ]
  edf$Term = gsub("RHEUMA SEROPOS OTH", "", edf$Term)
  edf$Term = gsub("pathway \\(", "pathway\n(", edf$Term)
  edf$Term = gsub(" and cytokine", "\nand cytokine", edf$Term)
  edf$Term = gsub(" by antimicrobial", "\nby antimicrobial", edf$Term)
  edf$Term = gsub("seropositiver", "seropositive r", edf$Term)
  edf$Term = Hmisc::capitalize(tolower(edf$Term))

  edf = edf[order(edf$P.value, decreasing = T), ]
  edf = edf[! duplicated(edf$Term), ]
  edf$Term = factor(edf$Term, levels=as.character(edf$Term))
  edf = edf[edf$P.value <= 0.01, ]

  edf$logP = -log10(edf$P.value)

  df = data.frame(table(unlist(strsplit(tolower(edf$Term), " "))))
  df = df[! df$Var1 %in% tm::stopwords("en"), ]

  if(class(df) != "integer" ){
    wordcloud::wordcloud(words = gsub("\n|\\:", "", df$Var1), freq = df$Freq, min.freq = 2,
                         max.words=200, random.order=FALSE, rot.per=0.5, use.r.layout = T,
                         scale=c(2, 0.5),
                         #fixed.asp = F,
                         colors=brewer.pal(8, "Dark2"))
    wc <<- recordPlot()

    enrich=ggplot(edf, aes(x=logP, y=Term, fill=Combined.Score)) +
      geom_bar(stat="identity") + theme_classic() +
      labs(x=expression(-log[10]*'(P)'), y="", title=x) +
      scale_fill_continuous(low="red", high="midnightblue", limits=c(0, 2700)) +
      geom_vline(xintercept = 2, lty="dashed")

    return(list(enrich, wc))
  }
}))
```

```{r, fig.height=20, fig.width=14, cache=FALSE, eval=FALSE}
cowplot::plot_grid(plotlist=unlist(plot.list, recursive = F), align="hv",
                   hjust = 0, vjust = 1, ncol=2, nrow=6, rel_widths = c(5, 1))

# output to pdf
pdf("/media/gcpeac/R4RA_machine_learning/Data/feature_enrichment.pdf", height=25, width=15)

ggarrange(plotlist = unlist(plot.list, recursive=F)[seq(1, length(unlist(plot.list, recursive=F)), 2)],
          ncol=2, nrow=3, align="hv", common.legend = T)
dev.off()
```



# Output Results

```{r}
save_output = FALSE
library(openxlsx)

if(save_output){
  save.image("/media/gcpeac/R4RA_machine_learning/Data/best_models_da.rdata")
  
  # save the tuning parameters for the optimal models
  models_list = list("Initial Rituximab"=rtx_bl_other_filt_plots[[1]],
                     "Initial Tocilizumab"=toc_bl_other_filt_plots[[1]],
                     
                     # "Final Rituximab"=rtx_other_filt_plots[[5]],
                     # "Final Tocilizumab"=toc_other_filt_plots[[1]],
                     "Refractory"=any_other_filt_plots[[1]]
  )
  names(models_list) = paste(names(models_list), "-",
                             unlist(lapply(models_list, function(x) x$fit$method)))
  write.xlsx(x = lapply(models_list, function(x) x$bestTune),
             rowNames=TRUE, overwrite = T,
             file = "/media/gcpeac/R4RA_machine_learning/Data/best_tune_fits.xlsx")
  
  
  # save features (by importance/coefficients)
  write.xlsx(x = lapply(models_list, function(x) {
    if(class(x$coefficients$data) != "waiver"){
      df = x$coef[, c("gene", "coef")]
      df = df[df$coef != 0, ]
      colnames(df) = c("Feature", "Coefficients")
      return(df)
    } else{
      df = x$vi[, c("gene", "Overall")]
      colnames(df) = c("Feature", "Variable Importance")
      return(df)
    }
  }),
  rowNames=FALSE, overwrite = T,
  file = "/media/gcpeac/R4RA_machine_learning/Data/coef_vi.xlsx")
  
  
  # output model summaries
  cs = c('model', 'filtering', 'drug','AUC', 
         'Accuracy', 'final_k', 'sparce_k', 
         'Precision', 
         'Youden_sensitivity', 'Youden_specificity')
  
  di = df_initial_response[, cs]
  di$drug = c("rtx"="Rituximab", "toc"="Tocilizumab", "any"="Refractory")[di$drug]
  di$filtering = c("uni"="Univariate", "none"="None")[di$filtering]
  di[, apply(di, 2, function(x) {all(! is.na(as.numeric(x)))})] =
    apply(di[, apply(di, 2, function(x) {all(! is.na(as.numeric(x)))})], 2,
          function(y) format(as.numeric(y), digits=3))
  colnames(di)[grepl("_k", colnames(di))] = c("Number of input features", 
                                              "Number of sparse output features")
  colnames(di) = Hmisc::capitalize(colnames(di))
  
  df = df_final_response[, cs]
  df$drug = c("rtx"="Rituximab", "toc"="Tocilizumab", "any"="Refractory")[df$drug]
  df$filtering = c("uni"="Univariate", "none"="None")[df$filtering]
  df[, apply(df, 2, function(x) {all(! is.na(as.numeric(as.character(x))))})] =
    apply(df[, apply(df, 2, function(x) {all(! is.na(as.numeric(as.character(x))))})], 2,
          function(y) format(as.numeric(y), digits=3))
  colnames(df)[grepl("_k", colnames(df))] = c("Number of input features", 
                                              "Number of sparse output features")
  colnames(df) = Hmisc::capitalize(colnames(df))
  df = df[df$Drug == "Refractory", ] 
  
  
  out = rbind(di, df)
  out = out[c(which(out$Drug == "Rituximab"), 
              which(out$Drug == "Tocilizumab"), 
              which(out$Drug == "Refractory")), ]
  colnames(out) = gsub("_", " ", colnames(out))
  
  write.xlsx(x = out, #list("Initial response"=di, "Final response"=df),
             rowNames=FALSE, overwrite = T,
             file = "/media/gcpeac/R4RA_machine_learning/Data/all_models.xlsx")
}

```